Heavy-Tailed Innovations in the \proglang{R} Package \pkg{stochvol}

### 2016-02-18 inst/doc/heavytails.Rnw
version 1.2.3

%% The address of (at least) one author should be given
%% in the following format:
\Address{
  Gregor Kastner\\
  Institute for Statistics and Mathematics\\
  Department of Finance, Accounting and Statistics\\
  WU Vienna University of Economics and Business\\
  Welthandelsplatz 1, Building D4, Level 4\\
  1020 Vienna, Austria\\
  E-mail: \email{gregor.kastner@wu.ac.at}\\
  URL: \url{http://www.wu.ac.at/statmath/en/faculty_staff/faculty/gkastner/}
}

>>>>

%% The address of (at least) one author should be given
%% in the following format:
\Address{
  Gregor Kastner\\
  Institute for Statistics and Mathematics\\
  Department of Finance, Accounting and Statistics\\
  WU Vienna University of Economics and Business\\
  Welthandelsplatz 1, Building D4, Level 4\\
  1020 Vienna, Austria\\
  Telephone: +43/1/31336-5593\\
  Fax: +43/1/31336-90-5593\\
  E-mail: \email{gregor.kastner@wu.ac.at}\\
  URL: \url{http://statmath.wu.ac.at/~kastner/}
}
